\documentclass[11pt]{article}
\usepackage[margin=0.8in]{geometry}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{hidelinks}
\setlength{\parindent}{0pt}
\setlength{\parskip}{5pt}
\begin{document}
\begin{center}
{\Large\bfseries V11 Final Validity and Claims Audit}\par
\vspace{4pt}
{\large Future Internet submission candidate}\par
\end{center}

\textbf{Status: PASS.} All 56 automated checks passed.

\section*{Headline findings}
\begin{itemize}
\item The compact trace file has 100 public-viewer records, 95 with positive token counts, divided chronologically into 60 search and 35 certification records.
\item The locked absolute-SLO study certifies 0 of 120 method runs. Universal abstention is retained as a negative result.
\item The separately locked independent-seed noninferiority follow-up certifies 50/60 DR-BGS runs and 33/60 guarded-GP runs.
\item Every certified noninferiority run exactly recovers the exhaustive training-selected policy. This is retrospective validation, not a deployable optimality certificate.
\item Search plus certification uses 83.95\% fewer replications than exhaustive training evaluation plus the same certification batch.
\end{itemize}

\section*{Validity boundary}
Arrival times and token counts are trace-derived. Privacy labels, pressure conversion, and moving-block replay are synthetic. The study uses a compact public slice rather than the full BurstGPT corpus. Exact binomial bounds are conditional on independent simulator replays from the declared generator. They are not claims about live production safety. The follow-up was designed after the strict-study result and is not described as external confirmation.

\section*{Key numerical checks}
\begin{tabular}{lr}
\toprule
Quantity & Audited value\\
\midrule
Trace rows / positive rows & 100 / 95\\
Policy surfaces & $12\times190=2{,}280$\\
Strict method runs & 120\\
Absolute certified runs & 0\\
DR-BGS noninferiority certified & 50/60\\
Guarded-GP noninferiority certified & 33/60\\
Search+certification reduction & 83.9506\%\\
Python sources compiled & all\\
Missing or unused citations & none\\
Overfull boxes & none\\
\bottomrule
\end{tabular}

\section*{Provenance checks}
The primary configuration, compact trace CSV, and execution code match the archived SHA-256 values. A portable chronology snapshot preserves the working archive metadata used to record that the primary lock preceded strict result generation and that the follow-up lock preceded its result files. This establishes internal archive chronology and tamper detection; it is not third-party preregistration or trusted timestamping.

\section*{Language and claims}
Selected promotional and formulaic markers were absent. The manuscript states the failed absolute certificate directly, avoids the term ``breakthrough,'' and distinguishes deployment certification from retrospective comparison with an exhaustive reference.

\section*{Conclusion}
The V11 manuscript and its trace-risk results are internally consistent. The scientific package is suitable for external review after the public repository and archival DOI are activated and verified.

\end{document}
